---
title: "Google restaurant reviews in Kuala Lumpur, Petaling Jaya and Shah Alam, Malaysia"
subtitle: "Part one"
author: "Sean Ng"
organization: "AIMdata"
date-modified: "12 December 2025"
execute: 
  echo: false
---


```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, 
                      message = FALSE, 
                      fig.width = 9)

library(tidyverse)
library(here)
library(janitor)
library(scales)
library(tidytext)
library(widyr)
library(ggraph)
library(patchwork)
library(kableExtra)
library(fuzzyjoin)
library(viridis)
library(textdata)
library(DT)

`%out%` <- Negate(`%in%`)
options(scipen = 100)
theme_set(theme_light())
range_wna <- function(x){(x-min(x, na.rm = TRUE))/(max(x, na.rm = TRUE)-min(x, na.rm = TRUE))}

Mode <- function(x) {
  ux <- unique(x)
  ux[which.max(tabulate(match(x, ux)))]
}
```


```{r data}
google_reviews <- read_csv("./data/GoogleReview_data_cleaned.csv") |> clean_names()

trip_reviews <- read_csv("./data/TripAdvisor_data_cleaned.csv") |> clean_names() |> 
  mutate(review = str_replace_all(review, "dim sum|Dim Sum|Dim sum", "dimsum"))
```

## Introduction and overview

A common refrain for this postmodern age is that online reviews are useless.

Today, we're looking at two different sets of scraped data to see to what extent that is true. Restaurant reviews from Google and Trip Advisor in Malaysia were scraped by [Ng Choon Khon](https://www.kaggle.com/datasets/choonkhonng/malaysia-restaurant-review-datasets) using the Selenium library. 

Below, we've plotted out the restaurants found in both datasets according to the number of reviews and their mean rating. Immediately, we note an unnatural pattern in the Google dataset: Google limits Selenium to only being able to scrape around 300 reviews per restaurant, at most.

Whilst this impacts and limits the dataset, we should still make the best use of it we can: Google's official API only allows five reviews to be extracted per restaurant because data freely given to the world must be paywalled and sold back to you.


<br>

```{r histogram, fig.width=9}
google_reviews |> 
  filter(location %in% c("Petaling Jaya", "KL")) |> 
  count(restaurant) |> 
  ggplot(aes(x = n)) + 
  geom_histogram(binwidth = 1/30, 
                 fill = "#6a994e") + 
  # geom_freqpoly(colour = "blue", alpha = .3) +
  scale_x_log10(breaks = c(0, 10, 30, 100, 300, 1000), 
                labels = comma) + 
  labs(title = "Google reviews per restaurant", 
       subtitle = "Largely limited to 300 reviews per restaurant",
       x = "Number of reviews", 
       y = "Number of restaurants") +

trip_reviews |> 
  filter(location %in% c("Petaling Jaya", "KL")) |> 
  count(restaurant) |> 
  ggplot(aes(x = n)) + 
  geom_histogram(binwidth = 1/30, 
                 fill = "#6a994e") + 
  # geom_freqpoly(colour = "blue", alpha = .3) +
  scale_x_log10(breaks = c(0, 10, 30, 100, 300, 1000), 
                labels = comma) + 
  labs(title = "Trip Advisor reviews per restaurant", 
       subtitle = "No limits for number of reviews scraped",
       x = "Number of reviews", 
       y = "Number of restaurants") +

  plot_annotation(
    title = "The Trip Advisor reviews dataset has a much more natural distribution"
  )

```

<br>

Google reviews are sorted by default by "relevance", so it is only possible to say that this was determined by a combination of recency, quality (word count, images) and whether or not a review was regarded by the community as helpful. 

```{r malay-list}
# Maybe someone with a better grasp of Malay can improve on this, 
# But it works pretty well as long as the not_malay_list is run as well
# The number for Trip Advisor is likely lower still, since there were still some false positives
malay_list <- " yang|sedap|makanan|Makanan| saya| Saya|dulu|semua|kali|sdap|sangat|Sangat|lauk|harga|tapi|terbaik|berbaloi| dgn|siap|tidak|bole|boleh| lain|cantik"

# Not really that surprising that "kalian" is almost always just a mispelling of "kailan", 
# But I'll leave it out as it could make too many false negatives
not_malay_list <- "yangzhou|yang zhou|Yang zhou|wayang|Wayang|tapioca|Tapioca|Gansayam|Rasa Saya|ying yang|yin yang|goyang|fried rice|chargable|hargao"

malay_pc_summary <- rbind(google_reviews |>
  filter(!is.na(review)) |> 
  mutate(malay = ifelse(
  str_detect(review, malay_list) & 
    !str_detect(review, not_malay_list), 1, 0)) |> 
  summarise(count = n(), 
            malay = sum(malay)) |> 
  mutate(malay_pc = round(malay / count * 100, 2), 
         source = "Google"),

trip_reviews |> 
  filter(!is.na(review)) |> 
  mutate(malay = ifelse(
  str_detect(review, malay_list) & 
    !str_detect(review, not_malay_list), 1, 0)) |> 
  summarise(count = n(), 
            malay = sum(malay)) |> 
  mutate(malay_pc = round(malay / count * 100, 2), 
         source = "TripAdvisor"))

```



Let's review the limitations once more, before we look into these datasets: 

* Google's dataset is not a representative sample of reviews, as many restaurants only have the first 300 most "relevant" reviews. Google reviews, in general, are less policed, with numerous instances of  [scams]((https://www.asiaone.com/lifestyle/restaurant-ibid-woo-wai-leong-police-reviews-scam)) and fake reviews.  

* Both Google maps and Trip Advisor are principally English language platforms when it isn't spoken by the majority of the population. Upon a cursory inspection, there are very few reviews in Malay or with Malay words in Google (`r malay_pc_summary |> filter(source == "Google") |> pull(malay_pc)`%) and even less in Trip Advisor (`r malay_pc_summary |> filter(source == "TripAdvisor") |> pull(malay_pc)`%). This is extremely different from even urban demographics where there are proportionally more minorities, though this skew is more understandable on Trip Advisor than on Google. 

* The price range is missing from this data. This is unfortunate because price is one of the main topics mentioned in reviews. 

* These reviews were extracted three years ago: some of these restaurants have closed. Before we re-scrape the data and update these datasets, let's see what is of most in the existing data (which was used to make a sentiment analysis app). 

The purpose of this series of analyses is to better understand Google and Trip Advisor's rating systems in order to better interpret reviews and choose better restaurants. 

Because whilst reviews themselves were meant to be informational, expressive or cautionary, the platforms are mired in layers of obfuscation, gamification and marketing; additionally, all reviews are affected by prevailing social mores (we will discuss below the skew towards five stars). This leads me to question that despite all the data we have, how much about restaurant reviews will be actually quantifiable. 

<br><br><br>


## Adding cuisine

These are the columns present in the Google dataset: 

```{r}
google_reviews |> 
  colnames() 

```

Trip Advisor has additional columns for `review title` and `date`. 

Let's add a column for cuisine (the code can be downloaded at the top of the page, but it was a lot of manual work) to increase interpretability and to maximise the usefulness of the data. We'll narrow down the scope to locations in the Klang Valley (KL, PJ and Shah Alam, in the datasets; since I'm most familiar with and most interested in this metro).  



```{r buffet-fusion-lists}

trip_buffet_list <- trip_reviews |> 
  mutate(possible_buffet = ifelse(
    str_detect(review, "Buffet|buffet") | 
      str_detect(title, "Buffet|buffet") |
      str_detect(restaurant, "Buffet|buffet")
    , 1, 0), 
    count = 1) |> 
  group_by(restaurant) %>% 
  summarise(reviews = sum(count), 
            buffet_count = sum(count[possible_buffet == 1])) |> 
  arrange(desc(buffet_count)) |> 
  mutate(buffet_pc = buffet_count / reviews) |> 
  mutate_at(vars(reviews, buffet_count, buffet_pc), ~range_wna(.)) |>  
  mutate(buffet_score = (buffet_count + buffet_pc) / 2) |> 
  arrange(desc(buffet_score)) |> 
  filter(buffet_score >= .2) |> 
  pull(restaurant)

trip_fusion_list <- trip_reviews |> 
  mutate(possible_fusion = ifelse(
    str_detect(review, "Fusion|fusion") | 
      str_detect(title, "Fusion|fusion") |
      str_detect(restaurant, "Fusion|fusion")
    , 1, 0), 
    count = 1) |> 
  group_by(restaurant) %>% 
  summarise(reviews = sum(count), 
            fusion_count = sum(count[possible_fusion == 1])) |> 
  arrange(desc(fusion_count)) |> 
  mutate(fusion_pc = fusion_count / reviews) |> 
  mutate_at(vars(reviews, fusion_count, fusion_pc), ~range_wna(.)) |>  
  mutate(fusion_score = (fusion_count +  fusion_pc) / 2) |> 
  arrange(desc(fusion_score)) |> 
  filter(fusion_score >= .11) |> 
  pull(restaurant)

google_buffet_list <- google_reviews |> 
  mutate(possible_buffet = ifelse(
    str_detect(review, "Buffet|buffet") | 
      str_detect(restaurant, "Buffet|buffet")
    , 1, 0), 
    count = 1) |> 
  group_by(restaurant) %>% 
  summarise(reviews = sum(count), 
            buffet_count = sum(count[possible_buffet == 1])) |> 
  arrange(desc(buffet_count)) |> 
  mutate(buffet_pc = buffet_count / reviews) |> 
  mutate_at(vars(reviews, buffet_count, buffet_pc), ~range_wna(.)) |>  
  mutate(buffet_score = (buffet_count + buffet_pc) / 2) |> 
  arrange(desc(buffet_score)) |> 
  filter(buffet_score >= 0.1764) |> 
  pull(restaurant)

google_fusion_list <- google_reviews |>
  mutate(possible_fusion = ifelse(
    str_detect(review, "Fusion|fusion") |
      str_detect(restaurant, "Fusion|fusion")
    , 1, 0), 
    count = 1) |> 
  group_by(restaurant) %>% 
  summarise(reviews = sum(count), 
            fusion_count = sum(count[possible_fusion == 1])) |> 
  arrange(desc(fusion_count)) |> 
  mutate(fusion_pc = fusion_count / reviews) |> 
  mutate_at(vars(reviews, fusion_count, fusion_pc), ~range_wna(.)) |>  
  mutate(fusion_score = (fusion_count +  fusion_pc) / 2) |> 
  arrange(desc(fusion_score)) |> 
  filter(fusion_score >= .11) |> 
  pull(restaurant)
```



```{r reviews-cuisine-cleaning}

reviews_cuisine_cleaning <- function(tbl) {
  
  tbl |> 
    # Not a specific restaurant
    filter(restaurant %out% c("Jalan Alor", "Sham's Cooked With Love", "Hawker Stalls in Chinatown",
                              "Feast Village Starhill Gallery", "ICC Pudu", "Imbi Market", 
                              "Taste of Asia", "Thirty8 Fashion", "Happy Mansion")) |> 
    # Some cleaning 
    mutate(restaurant = str_replace(restaurant, "Birch", "Huckleberry")) |> 
    mutate(restaurant = str_replace_all(restaurant, "Passage thru'", "Passage Thru"),
           restaurant = str_replace_all(restaurant, "Gravybaby", "GravyBaby"), 
           restaurant = str_replace_all(restaurant, "Ploy", "PLOY"), 
           restaurant = ifelse(restaurant == "What Tasty Food", "WTF - What Tasty Food", restaurant),
           restaurant = ifelse(restaurant == "ATAS", "ATAS at The RuMa Hotel & Residences", restaurant), 
           restaurant = ifelse(restaurant == "Al Rawsha Restaurant Kuala Lumpur", "Al Rawsha Restaurant", restaurant), 
           restaurant = ifelse(restaurant == "Aliyaa", "Aliyaa Island Restaurant & Bar", restaurant), 
           restaurant = ifelse(restaurant == "Arthur's Bar & Grill, Shangri-La Hotel, Kuala Lumpur", 
                               "Arthur's Bar & Grill", restaurant), 
           restaurant = ifelse(str_detect(restaurant, "Lemon Garden"), 
                               "Lemon Garden", 
                               restaurant), 
           restaurant = ifelse(str_detect(restaurant, "Din Tai Fung at The Gardens Mall"),
                               "Din Tai Fung at The Gardens Mall", 
                               restaurant), 
           restaurant = ifelse(restaurant == "Monnalisa Italian Restaurant", 
                               "Monnalisa Ristorante Italiano", 
                               restaurant), 
           restaurant = ifelse(str_detect(restaurant, "Fatty Mee Hoon Kuih"), 
                               "Fatty Mee Hoon Kuih", 
                               restaurant), 
           restaurant = ifelse(str_detect(restaurant, "Whisky Bar KL"), 
                               "The Whisky Bar", 
                               restaurant), 
           restaurant = str_replace_all(restaurant, "W XYZ", "WXYZ"), 
           restaurant = ifelse(restaurant == "The Daily Grind Bangsar", 
                               "The Daily Grind", 
                               restaurant), 
           restaurant = ifelse(restaurant == "Chili's 1 Utama", "Chili's", restaurant), 
           restaurant = str_replace_all(restaurant, "Merini", "Marini"))  |>
    mutate(
      cuisine = case_when(
        
        # The order of the case_when statements is important. Particularly, it should go
        # South Asian -> Buffet -> Fusion,
        # This is because I would consider South Asian buffet restaurants as South Asian.
        # And I would not consider hotel buffets to be a type of fusion restaurant, 
        # despite all the types of food they might serve.
        # Also, Grill before Bar.
        
          str_detect(
          restaurant,
          "Grill|Steakhouse|Grub|Steak|Brasserie|steakhouse|BBQ|Rock Salt Restaurant|BBP|Churrascaria|Marble 8|Beast|Nando's|Nandos|Bar B Q|Down to Bones|Barbecue|Vantador|Bbq|Butcher Carey|PRIME|Brasserie|Karnivormalaya|Chamber's"
        ) ~ "Grill",
          str_detect(restaurant,
          "Bistro|Deli|Secret Recipe|Tujo|Wild Sheep|Antipodean|Coffee|One Half|Blue Room|Awesome Canteen|Botanica|Chili's|Don's Diner|GravyBaby|Hornbill|Huck's|myBurgerLab|Naj & Belle|Tony Roma's|Louisiana|Cor Blimey|4Fingers|Bacon And Balls|POP PIZZA|After Black|Ashley's by Living Food|March Azalea Kitchen|Mighty Monster IPC|Sköhns Canteen|Table9|Rabbit Hole|Williams Corner|Tiki Taka|4 Fingers|Ben's|Souled Out|Suzi's Corner|Fuel Shack Signature|SOULed OUT|TGI Friday|Chilli's|Pigs & Wolf|Ship|Breakfast Thieves|Ante|Morganfield's|Subway|Meat The Porkers|Pan & Tamper|Hubba Mont Kiara|Bacon & Balls|Tate|Gin Ger|Fuel Shack|Jarrod & Rawlins|BreadFruits|Glass Tartines and Tipples|B-Lab|Mighty Monster|Ticklish Ribs|Cozy Corner|Duddha|Fat Brother|Define:food|Tangerine|Sausage & Ribs Shack|Texas Chicken|Coco Fika|Andra By Gula Cakery|D Place|Chef Zubir|Hubz|Maipi Corner|Marrybrown|Meet and Meat|Jibby & Co|Midwest|WhupWhup|Foodilicious Kitchen Shah Alam|Craveat"
        ) ~ "Casual Western",
        str_detect(
          restaurant,
          "Chinese|Taiwan|[\\p{Han}]|Nam Heong|Dynasty|Putien|Hoi|Gold Dragon|Han Room|Village Duck|Village Roast Duck|Unique|Steamboat|Ah |Roast Pork|Hokkien Mee|Dim Sum|Lai Po Heen|Yun House|Chynna|Li Yen|Shanghai|Lai Foong|Little Penang Kafé|Goon Wah|Shang Palace|YEN|Yut Kee|Din Tai Fung|Dragon-i|Celestial Court|The Ming Room|Sai Woo|Luk Yu|Yue|Way Modern Chinois|Hong Kong|Blue Boy Vegetarian Food Centre|Xin|Lai Ching Yuen|Noble House|Noodle House|Bak Kut|Fong Lye|Wan Tan Mee|Sarawak Laksa|Hakka|Ruyi & Lyn|Chicken rice|Chicken Rice|Char Siew|Siew Yoke|Dim Sum|Chiu Chow|Hainan|Hailam|Pork Noodles|Koong Woh Tong|Yong Tow Foo|Madam Tang| Kee|The Pot KL|Yu Noodle Cuisine|Wan Chun Ting|Muk Koot|Oversea|Marco Polo|Cu Cha Restaurant|Imperial|Grand Harbour|In Colonial Restaurant|Museum Restaurant|Heng|Hiong Kong|Ban Lee Restaurant|Heong|Restaurant Mama Love|Hee Lai Ton|New Paris|Kingdom Palace|Siu Siu|Sam You|Ti Chen|Mee Hoon|Fishball|Peoh|Esquire|Restourant Boston|7th Mile Kitchen"
        ) ~ "Chinese",
        str_detect(
          restaurant,
          "Italia|Olive|Ristorante|Osteria|Prego|Pizza|Trattoria|Nero Nero|Positano|a'Roma|Vin's Restaurant|Michelangelo|Marini's|Nizza|Porto Romano|Tatto|Neroteca|La Risata|Portofino|Ciao|Enoteca|Mangiare|Sassolino|Pizzeria|La Casa Restaurant & Patisserie|Favola|Senja Restaurant|Graze"
        ) ~ "Italian",
        str_detect(
          restaurant,
          "German|French|Chez|Marta's|Tapas|Bistro à Table|Iberico|El Toro Loco|Petit|Mercat|Dominic|El Cerdo|Quivo|Skillet KL|iberico|Yeast|Maison Francaise|El Mesón|Lafite|Topshelf|Wurst|Sabayon|Chateau|Naughty Babe Dirty Duck|Hit & Mrs|Le Gourmandin|Soleil|Suisse|IKEA|Leonardo|MARCO Creative Cuisine|Abanico|La Belle Saison"
        ) ~ "European",
        str_detect(restaurant, "Thai|Bangkok|BKK|Baan|Tamarind Springs|Chakri|BAAN|Samira by Asian Terrace|Ekkamai|Busaba|Mamasan|Krung Thep|Tomyam|Aroma Restaurant|Chef Korn|Tuk Tuk"
                   ) ~ "Thai",
        str_detect(restaurant, "Arab|Turkish|Al-|Halab|Egyptian|Tarbush|Wadi|Sahara Tent|Shawarma|Damascus|Syria|Hadramawt|diafah|Iraq|Sarifa|Al Rawsha|The Castle Restaurant|Saba Restaurant|Marhaba|ALRAWSHA Restaurant|Antara|Andalus|El Sham|Oregi Restaurant"
                   ) ~ "Levantine",
        # Malay (Chef Wan) and Malaysian (Madan Kwan's)
        str_detect(
          restaurant,
          "Malay|Rasa|Cik|Dapur|Rebung|Zakhir|Village Park|ADU|Warisan|Nasi|Dancing Fish|Sarang|Bijan|Serai|Sambal|ATAS|Grandmama's|Onde Onde|JP teres|Satay Station|Chef Wan|De.Wan|Siti Li Dining|Pintu|Ramly|Penyet|Sepiring|Satay|Restoran Ali Food Corner|Open House|Sup Utara|Bawal Power|Ikan|Gulai|Kampung Mu|Marlina Station|Wong Solo|Bawang|Goreng"
        ) ~ "Malay",
        str_detect(
          restaurant,
          "Nonya|Baba|Mum's Place|Madam Kwan|Chuup|Old China Cafe|Nyonya|Little Penang|Oriental Cravings|Papparich|Uncle Don|Muar Restaurant|Kumi|Peranakan|1919 Restaurant"
        ) ~ "Malaysian",
        str_detect(
          restaurant,
          "Japan|Edo|Sushi|Kampachi|Iketeru|Menya|Nobu|Omakase|TOKYO|Tokyo|Tonkatsu|Udon|Soba|Ichibanya|Maruhi|Omulab|Zipangu|Miyabi|Izakaya Hanazen|hokkaido|Senya|IPPUDO|Umai-Ya|Ichiban|Yakiniku|Nihon|Lucky Tora|Hokkaido|Mo-Mo Paradise|Sushi|sushi|Uokatsu|Ramen|Tempura|Izakaya|Tokyo|Kyoto|Oishii|Gyoza|Ichiban|Tonkotsu|Tonkatsu|Sakura|Yakitori|Kyush|Teppanyaki|Taka|Kikubari|Ichiyutei|Enju|Okonomi|Toridoki|Syokudo|Tsukiji|Yuzu|Madam Salma|Fu-Rin"
        ) ~ "Japanese",
        # Why not merge all Korean BBQ into grill?
        str_detect(
          restaurant,
          "Filipino|Bali|Vietnam|GOODDAM|Korea|Sao Nam|Naughty Nuri's|KyoChon|Viet|Dakgalbi|Sopoong|Kung Jung|Saigon|Sae Ma Eul|KoRyo-Won|Koryowon|Persia|Astana|Buns & Noodles|Kyochon|Topokki"
        ) ~ "Other Asian",
        
        # Do not str_detect(.x, "bar")
        str_detect(restaurant, "Whisky|Lounge|Bar|Decanter|Knowhere Bangsar|The Locker & Loft|Tom, Dick & Harry's|WET|The Enclave|Out of Africa|Opium|THIRTY8|Healy Mac's|TEMPTationS|Loco bar|La Bodega|Vertigo|The Social|No Black Tie|The BAR|O'Galito|Table 23|D Legends bar|Bobo KL|Rock Bottom|twenty-one kitchen+bar|Bentley's Pub|Vinh City Entertainment|twenty-one|Malones|White Horse Tavern|Supperclub KL|Backyard|The Ceylon bar|W1 Dining & Cocktails|Splash|Drop Exchange|Boardwalk|Deep Blue|The Sticky Wicket|OneSixFive|The Attic|Concubine KL|The Green Man|THE BAR|Marini’s on 57|Rooftop 25"
        ) ~ "Bar",
        str_detect(restaurant, "Cafe|Grind|Café|Tujo|cafe|Alexis|The Loaf|Yellow Brick Road|Huckleberry|TWG|Newens Tea House|Miss Ellie Tea House|Frisky Goat|Urbean|Ra-Ft|Backofen|STG Bukit Ceylon|VCR|Rise & Shine by Tapestry|Kafe|Kaffe|Kopi|Latte|Kopitiam"
        ) ~ "Cafe",
        str_detect(
          restaurant,
          "Kerala|India|Lanka|Malabar|Curry|Raju|Bhavan|Thosai|Tandoor|Bombay|Gem Restaurant|Nasi Kandar|NADODI|Qureshi|RSMY|Sangeetha|Nirwana|Asian Rice Pot|Masala|Annalakshmi|Aliyaa|MTR|Devi's Corner|WTF - What Tasty Food|Nadodi|Delhi Royale|FLOUR|Bakti Woodlands|Vishal Food|Banana Leaf|Hyderabad|sarvana bhavan|Spice Garden|Roti|TasteBud|Chapati|Pakistani|Jai Hind|BananaBro|Naan|SK Corner|Sri Paandi|Majapahit|Nan |GinRikSha|Briyani|Biryani|Maju Palace|Seetharam|Havelly|Punjab|Goa By Sapna Anand|Swaadisht|Mamak|Sri|Chapathi|Moghul|Rani|Aryan|Yarl|Sagar|ABC Foods Corner|Sheesh Mahal|Mallikas"
        ) ~ "South Asian",
        
        # Buffet list
        restaurant %in% trip_buffet_list ~ "Buffet",
        restaurant %in% google_buffet_list ~ "Buffet", 
        str_detect(restaurant, "Flock, W Kuala Lumpur|HYdeout By Grand Hyatt Kuala Lumpur|Curate"
                   ) ~ "Buffet", 
        # List of fusion restaurants
        restaurant %in% trip_fusion_list ~ "Fusion",
        restaurant %in% google_fusion_list ~ "Fusion", 
        str_detect(restaurant, "Symphony by Chef Jo|Darren Chin|Dewakan|DC Restaurant|Sitka|Ginger Restaurant|Table & Apron|Foodsbury"
                   ) ~ "Fusion", 
        
        # Unfortunate, there aren't enough Latino restaurants for their own category
        str_detect(restaurant, "Latino|Mexican|Carretas|Mexico|Frontera|Mexicana|Cocina"
        ) ~ "Other",
        str_detect(restaurant, "Oliver Gourmet|Seafood|Shell Out|BAIT|Fisherman|Fish & Co|Shucked|Delay No More Crab Restaurant|Ombak"
        ) ~ "Seafood",
        str_detect(restaurant, "Vasco's|Latest Recipe|Lemon Garden|Prime|Gastro Sentral|Chinoz On The Park|Shook|Plane In The City|Contango|The Living Room|Curate At Four Seasons|Beta KL|CEDAR on 15|The Apartment|The Grand Getaway|Strato|Ril's|Chocha|Wizards at Tribeca|Nipah|Joloko|Leonardo's Dining Room & Wine Loft|Roofino Skydining|Troika|Dining In The Dark KL|PLOY|Atlas Gourmet Market|WIP|Nathalie Gourmet Studio|Altitude|The Canteen by Chef Adu|Latitude 03|The Orchid Conservatory|Graze Restaurant|Zende Restaurant|Crystal|Cielo KL|Cedar On 15"
        ) ~ "Other Upmarket",
        # Just mopping up all the Dai Chow
        # I feel this is going to create problems down the line
        str_detect(restaurant, "Restoran"
        ) ~ "Chinese",
        TRUE ~ "Other"
  )) |> 
    mutate(rowid = row_number())
}


```


```{r trip-kl-cuisine and google-kl-cuisine}
trip_kl_cuisine <- trip_reviews |> 
  filter(location %in% c("KL", "Petaling Jaya", "Shah Alam")) |> 
  reviews_cuisine_cleaning() 

google_kl_cuisine <- google_reviews |> 
  filter(location %in% c("KL", "Petaling Jaya", "Shah Alam")) |> 
  reviews_cuisine_cleaning()

trip_kl_cuisine |> write_csv("./data/trip_kl_cuisine.csv")

google_kl_cuisine |> write_csv("./data/google_kl_cuisine.csv")

summary_stats <- rbind(
trip_kl_cuisine |>
  mutate(count = 1) |> 
  group_by(restaurant) |> 
  mutate(reviews = sum(count)) |> 
  ungroup() |> 
  filter(reviews >= 20) |> 
  summarise(mean_rating = mean(rating), 
            median_rating = median(rating), 
            mode_rating = Mode(rating)) |> 
  mutate(source = "Trip Advisor"),

google_kl_cuisine |>
  mutate(count = 1) |> 
  group_by(restaurant) |> 
  mutate(reviews = sum(count)) |> 
  ungroup() |> 
  filter(reviews >= 20) |> 
  summarise(mean_rating = mean(rating), 
            median_rating = median(rating),
            mode_rating = Mode(rating)) |> 
  mutate(source = "Google")
)
```


Determining the cuisine of a restaurant was mostly fairly obvious, and the categories hopefully self-explanatory. Additional notes on the coding of these cuisines may be found in the appendices. 

Let's start first with an overview of both datasets, now with cuisines included. From the plot below, we see that: 

* South Asian, Chinese, Casual Western, Japanese and Bars are the most commonly-reviewed restaurants in the Klang Valley. These are not the most commonly-visited restaurants.  

* Chinese, Casual Western, Malaysian and Thai are the lowest-rated cuisines. 

* Fusion, Other Upmarket (experiential dining or unspecified "international" cuisine) and bars have the highest ratings, with 60% or more of all reviews being five stars. 

* Trip Advisor and Google reviewers differ the most on their opinions of Levantine, Casual Western and Japanese restaurants. 

* The x-axes on the plots below show the percentage of reviews that are five stars by cuisine. This actually provides much more differentiation than just the mean rating, as we will discuss in the next section.


<br>


```{r fig.width=7}

google_kl_cuisine |> 
  mutate(count = 1) |> 
  group_by(cuisine) |> 
  summarise(reviews = n(), 
            five_star_reviews = sum(count[rating == 5]), 
            mean_rating = mean(rating)) |> 
  mutate(five_star_pc = five_star_reviews / reviews, 
         source = "Google")|> 
  select(five_star_pc, cuisine, source, reviews, mean_rating) |> 
  rbind(
    trip_kl_cuisine |> 
      mutate(count = 1) |> 
      group_by(cuisine) |> 
      summarise(reviews = n(), 
                five_star_reviews = sum(count[rating == 5]), 
                mean_rating = mean(rating)) |> 
      mutate(five_star_pc = five_star_reviews / reviews, 
             source = "Trip Advisor") |> 
      select(cuisine, five_star_pc, source, reviews, mean_rating)
  ) |> 
  ggplot(aes(x = five_star_pc, 
             y = fct_reorder(cuisine, mean_rating), 
             fill = mean_rating)) + 
  geom_col(alpha = .7) + 
  scale_x_continuous(labels = percent) +
  geom_text(aes(label = comma(reviews)), 
            position = position_dodge(width = .9), 
            hjust = "inward", 
            colour = "grey20") + 
  scale_fill_viridis(direction = -1, begin = .15, option = "turbo") +
  facet_wrap(~ source) + 
  theme(strip.background = element_rect(fill = "black"), 
        strip.text = element_text(face = "bold"),
        legend.title = element_text(size = 9), 
          legend.text = element_text(size = 7),
          legend.key.size = unit(0.9, "lines")) +
  labs(x = "% of reviews that are five-stars", 
       y = "", 
       title = "% of reviews that are five stars on Google and Trip Advisor, by cuisine", 
       subtitle = "Only restaurants in the Klang Valley. Total number of reviews at the end of each bar.", 
       fill = "Mean\nrating")
  

```

<br><br><br>

## Comparisons of average ratings

With reference to the histograms below, that ratings are skewed towards the higher end: the mean rating of restaurants on Google is **`r summary_stats |> filter(source == "Google") |> pull(mean_rating) |> round(2)`** and the mean rating on Trip Advisor is **`r summary_stats |> filter(source == "Trip Advisor") |> pull(mean_rating) |> round(2)`**. The median and mode for both datasets is **5**.  

It really could be said that the default review rating is five stars. This means that restaurant reviews on these platforms are very lax. It is hard for me to believe that half of all reviews were about a truly exceptional dining experience: **`r round(google_kl_cuisine |> filter(rating == 5) |> nrow() / nrow(google_kl_cuisine) * 100, 2)`%** of all ratings in the Google dataset for the Klang Valley are five stars; in Trip Advisor, it was **`r round(trip_kl_cuisine |> filter(rating == 5) |> nrow() / nrow(trip_kl_cuisine) * 100, 2)`%**. 

<br>

```{r}
compare_histograms <- function(tbl){
  tbl |> 
    mutate(count = 1) |> 
    ggplot(aes(x = rating, y = count)) + 
    geom_col(fill = "#6a994e") + 
    scale_y_continuous(labels = comma) + 
    labs(y = "Number of reviews", 
         x = "Rating")
}

google_kl_cuisine |> 
  compare_histograms() +
  labs(title = "Google ratings") +
  coord_flip() +

trip_kl_cuisine |> 
  compare_histograms() +
  labs(title = "TripAdvisor ratings") + 
  coord_flip() +
  
  plot_annotation(
    title = "Similar distributions of review ratings",
    subtitle = "Only includes restaurants in the Klang Valley."
  )


```

<br>

To take an immediate point of action, if a restaurant that you would like to try has a review summary chart more heavily weighted to the bottom than the charts above, it 

Given that reviews are limited to a one-to-five scale, there is not very much differentiation amongst how restaurants are rated. In the scatterplots below, we note restaurants that almost all restaurants mostly receive five stars (blue) or four stars (green). This means that neither Google nor Trip Advisor ratings are particularly useful at distinguishing between restaurants.

It might even be more useful to just have a ratio of five- and four-star reviews vs one-, two- and three-star reviews -- this could be 

The number of total reviews is correlated with mean rating. 


<br>


```{r restaurant-comparison-trip-google, fig.width=8, warning=FALSE, message=FALSE}

compare_google_trip <- function(tbl){
  
  tbl |> 
    group_by(restaurant, cuisine) |> 
    summarise(reviews = n(), 
              mean_rating = mean(rating), 
              median_rating = median(rating), 
              mode_rating = Mode(rating),
              .groups = "drop") |>  
    filter(reviews >= 20)
  }

plot_google_trip <- function(tbl){
  
  tbl |> 
    ggplot(aes(x = reviews, 
               y = mean_rating)) +
    geom_point(aes(colour = median_rating), 
               alpha = .4) + 
    # scale_size_continuous(limits = c(1, 10)) +
    scale_x_log10(labels = comma) +
    scale_colour_viridis(option = "turbo", begin = .15, end = .9, direction = -1, 
                         labels = label_number(accuracy = .1)) +
    # ggrepel::geom_text_repel(aes(label = cuisine)) + 
    geom_smooth(method = "lm", alpha = .1, size = 0, span = .5) + 
    geom_smooth(method = "lm", se = FALSE, alpha = .1, size = .2) + 
    labs(subtitle = "Restaurants with less than 20 reviews excluded", 
         x = "Number of reviews",
         y = "Mean Rating",
         colour = "Median Rating") +
    theme(legend.title = element_text(size = 9), 
          legend.text = element_text(size = 7),
          legend.key.size = unit(0.9, "lines"))
    
}
  

google_kl_cuisine |> 
  compare_google_trip() |> 
  plot_google_trip() + 
  # ylim(3.8, 4.6) +
  labs(title = "Google reviews") +
  guides(size = guide_legend(override.aes = list(alpha = 1))) +

trip_kl_cuisine |> 
  compare_google_trip() |> 
  plot_google_trip() + 
  # ylim(3.8, 4.6) +
  labs(title = "Trip Advisor reviews") +
  guides(size = "none") +
  
  plot_annotation(title = "Klang Valley restaurants and average ratings") +
  plot_layout(guides = "collect") & theme(legend.position = "bottom")

ggsave("./plots/cuisine_comparison_trip_google.png", height = 7, width = 11, units = "in")

```





<br><br><br>

### In both Google and Trip


Just having these two sets of reviews to examine, 

Are reviews useful? The commonality of five-star reviews indicate that the mean rating is more likely an indicator of expectations being met rather than any true excellence. 



These differences probably come down to the reviewers on Google and Trip Advisor and their respective purposes. Google reviewers are often locals or general consumers, whilst Trip Advisor reviewers tend to be travellers who have to provide more structured, specific reviews, leading to less casual reviews as there is a minimum word count required. 

<br>

```{r restaurant-fuzzy-match}

restaurant_fuzzy_match <- stringdist_join(
  trip_reviews |> 
    filter(location %in% c("KL", "Petaling Jaya", "Shah Alam")) |> 
    distinct(restaurant) |> 
    mutate(restaurant_match = str_remove_all(restaurant, "Restaurant|Cuisine|restaurant|Restoran|Curry House|Japanese"), 
           restaurant_match = trimws(restaurant_match)) |> 
    select(restaurant_trip = restaurant, 
           restaurant_match), 
  google_kl_cuisine |> filter(location %in% c("KL", "Petaling Jaya", "Shah Alam")) |> 
    distinct(restaurant)|> 
    mutate(restaurant_match = str_remove_all(restaurant, "Restaurant|Cuisine|restaurant|Restoran|Curry House|Japanese"),
           restaurant_match = trimws(restaurant_match)) |> 
    select(restaurant_google = restaurant, 
           restaurant_match), 
  by = "restaurant_match", 
  ignore_case = TRUE, 
  method = "jw",
  max_dist = 99, 
  distance_col = "dist"
) |> 
  group_by(restaurant_match.x) |> 
  slice_min(order_by = dist, n = 1) |> 
  arrange((dist)) |> 
  select(match_x = restaurant_match.x, 
         match_y = restaurant_match.y, 
         dist,
         restaurant_google, 
         restaurant_trip) |>
  ungroup()

both_google_and_trip <- restaurant_fuzzy_match |> 
  filter(match_x != "Teh Laris Cafe" | match_y != "Thosai Cafe") |> 
  filter(match_x != "The Ming Room" | match_y != "The Living Room") |>
  filter(match_x != "Cilantro & Wine Bar" | match_y != "ZENZERO & Wine Bar") |> 
  filter(match_x != "Kedai Kopi Pak Ngah" | match_y != "Kedai Kopi Lai Foong") |> 
  filter(match_x != "Shanghai" | match_y != "Old Shanghai") |> 
  filter(match_x != "Ah Ni Bak Kut Teh" | match_y != "Ah Sang Bak Kut Teh") |> 
  filter(match_x != "Pin Wei Seafood" | match_y != "Hoi Peng Seafood") |> 
  filter(match_x != "Cafe Cafe" | match_y != "Cafe ETC") |> 
  filter(match_x != "Tao Chinese" | match_y != "Ee Chinese") |>
  filter(match_x != "Seoul Garden" | match_y != "Lemon Garden") |>
  filter(match_x != "De.Wan" | match_y != "Dewakan") |>
  filter(dist <= 0.16666667)

combined_google_trip <- trip_kl_cuisine |> 
  filter(restaurant %in% both_google_and_trip$restaurant_trip) |> 
  select(cuisine, location, restaurant, rating, review) |>
  mutate(source = "TripAdvisor") |> 
  rbind(
    google_kl_cuisine |> 
      filter(restaurant %in% both_google_and_trip$restaurant_google) |> 
      select(cuisine, location, restaurant, rating, review) |> 
      mutate(source = "Google")
  ) |> 
  mutate(row_id = row_number()) |> 
  left_join(
    both_google_and_trip |> 
      distinct(restaurant_google, restaurant_trip) |>
      rename(restaurant = restaurant_trip),
    by = c("restaurant")
  ) |> 
  left_join(
    both_google_and_trip |> 
      distinct(restaurant_google, restaurant_trip) |>
      rename(restaurant = restaurant_google),
    by = c("restaurant")
  ) |> 
  mutate(restaurant_new = ifelse(!is.na(restaurant_google), 
                                 restaurant_google, 
                                 restaurant)) |> 
  group_by(row_id, location, cuisine, restaurant = restaurant_new, review, source) |> 
  summarise(rating = mean(rating), 
            .groups = "drop") |> 
  mutate(restaurant = trimws(restaurant))

```



```{r common-restaurants, fig.height=8, fig.width=10}
combined_google_trip |> 
  group_by(restaurant, source) |> 
  summarise(rating = mean(rating), 
          .groups = "drop") |> 
  pivot_wider(names_from = source, 
              values_from = rating) |> 
  left_join(
    combined_google_trip |> 
      count(restaurant, 
            name = "count"), 
    by = "restaurant"
  ) |> 
  left_join(
    combined_google_trip |> 
      distinct(restaurant, cuisine), 
    by = "restaurant"
  ) |> 
  filter(!is.na(Google) & !is.na(TripAdvisor)) |> 
  ggplot(aes(x = Google, y = TripAdvisor)) + 
  geom_smooth(alpha = .1, size = 0, span = .5, 
              method = "lm") + 
  stat_smooth(geom = "line", alpha = .1, size =.5, span = .5, 
              method = "lm") +
  geom_point(aes(colour = cuisine, 
                 size = count)) + 
  scale_colour_viridis_d(option = "turbo") +
  ggrepel::geom_text_repel(aes(label = restaurant), 
                           size = 1.2) + 
  labs(title = "Comparison between Google and TripAdvisor restaurant ratings", 
       subtitle = "Size indicates number of reviews", 
       y = "Trip Advisor mean rating", 
       x = "Google mean rating", 
       colour = "Cuisine", 
       size = "Review count") + 
  # guides(colour = guide_legend(override.aes = list(size = .7))) +
  theme(legend.title = element_text(size = 6), 
        legend.text = element_text(size = 6), 
        legend.key.size = unit(0.3, "lines"))

ggsave("./plots/restaurant_comparison_trip_google.png", height = 11, width = 11, units = "in")  
```

<br>

Google and TripAdvisor users seem to agree more than disagree. 

```{r new-rating-common-restaurants, fig.height=8, fig.width=10}

combined_google_trip |> 
  mutate(new_rating = ifelse(rating %in% c(5), 1, 0)) |> 
  group_by(restaurant, source) |> 
  summarise(new_rating = mean(new_rating), 
            .groups = "drop") |> 
  pivot_wider(names_from = "source", 
              values_from = new_rating) |> 
  left_join(
    combined_google_trip |> 
      count(restaurant, 
            name = "count"), 
    by = "restaurant"
  ) |> 
  left_join(
    combined_google_trip |> 
      distinct(restaurant, cuisine), 
    by = "restaurant"
  ) |> 
  filter(!is.na(Google) & !is.na(TripAdvisor)) |> 
  ggplot(aes(x = Google, y = TripAdvisor)) + 
  geom_smooth(alpha = .1, size = 0, span = .5) + 
  stat_smooth(geom = "line", alpha = .1, size =.5, span = .5) +
  geom_point(aes(colour = cuisine, 
                 size = count)) + 
  scale_colour_viridis_d(option = "turbo") +
  ggrepel::geom_text_repel(aes(label = restaurant), 
                           size = 1.2) + 
  xlim(0.2, .9) +
  ylim(0.2, .9) +
  scale_x_continuous(labels = percent, breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1)) + 
  scale_y_continuous(labels = percent, breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1)) +
  scale_size_continuous(breaks = c(100, 500, 1000, 2000)) +
  labs(title = "Comparison between Google and TripAdvisor using percentage of 5-star reviews", 
       subtitle = "Size indicates number of reviews.", 
       y = "% of 5-star ratings, Trip Advisor", 
       x = "% of 5-star ratings, Google", 
       colour = "Cuisine", 
       size = "Review count") + 
  # guides(colour = guide_legend(override.aes = list(size = .7))) +
  theme(legend.title = element_text(size = 6), 
        legend.text = element_text(size = 6), 
        legend.key.size = unit(0.3, "lines"))

ggsave("./plots/restaurant_comparison_new_ratings2.png", height = 9, width = 11, units = "in")  
```

<br>

Here we have replotted these restaurants. Behind the data is LOESS curve, which weights closer points more heavily; this helps in the detection of clusters.  

A five-star rating indicates that expectations have been met. 

Perhaps this combination of Google and Trip Advisor

Five-star

Nadodi has a michelin star 

It's possible that reviews are useless. 

Good service and environment can prevent a one-star review. 
Humans are crazy and feel debts viscerally. 
Separate food from service and waiters? But restaurants don't do that. 
Dining is an experience, and all aspects of the experience are vital. 

Is it fair to say that locals and more casual reviewers favour localised, 

Some deserve their four stars
Specialities can get you really far

This is one of those subjects where we all have experience. And that experience is applicable. 

For me, I see that the more localised, longstanding levantine (Bedouin and Istanbul) restaurants are much more popular on Google (with locals), rather than on Trip Advisor with many more expats and travellers. 


Maybe there should be separate scores for the food and the service? 
How do 


## Conclusions: Part one

Let's review what we've learnt from the datasets: 

* Reviews skew very heavily towards five stars. Roughly half of all reviews give five stars. This means that Google Maps and TripAdvisor should be used to decide where not to eat, as opposed as where to eat since five stars means a restaurant could mean anything from "met expectations" to "truly exceptional". Though much less numerous, one-, two- and three-starred reviews are much more informative than reading five star reviews. I will try sorting restaurant reviews by the lowest first, so I can avoid places that could be very disappointing. 

If you, like me, are unsatisfied with the lack of critique, it would be best to sort reviews by lowest first. 

* In fact, re-sorting your data will likely provide better results. Since you can also pay Google for visibility, looking at the tops results provides a very distorted view of the area in question. It is better to look through data without 

In spite of all this, I still haven't learnt anything that I instinctually did not know. In my day-to-day life, when engaging with online reviews, I'm still forced to engage with reviews individually, apart from the summary chart 

That the places where food is most commonly consumed, outside the home.

Outside of the home, hawker centres and coffee shops are places where food is most commonly consumed. Yet these businesses are not reviewed with anywhere the same frequency as the casual western eateries or chinese restaurants/*dai chows*. Food we consume every day is not subject to the same expectations as fine dining. But even more casual dining options warrant reviews. 

Or, the system could be skewed against hawkers. It is difficult to mark individual hawkers since they operate from within the premises of another business. Additionally, hawkers are much less likely to engage with Google or Trip Advisor to curate or market their online presence, leading to these platforms being blind to the needs of hawkers and continue to cater towards restaurants. Restaurants do spend on marketing (i.e. paying for visibility on Google Maps) 

The expectations around any restaurant, 

## Reference tables

```{r}
google_kl_cuisine |> 
  select(restaurant, cuisine, rating, location) |> 
  group_by(restaurant, cuisine, location) |> 
  summarise(mean_rating = round(mean(rating), 2), 
            reviews = n())
  glimpse()

trip_kl_cuisine |> 
  select(restaurant, cuisine, rating, location) |> 
  group_by(restaurant, cuisine, location) |> 
  summarise(mean_rating = round(mean(rating), 2), 
            reviews = n())
```








